\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{casual}
\moderncvcolor{red}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.75]{geometry}

\name{Son}{To}
\title{Resumé}
\address{Kuninkaantammenkierto 4 B 21}{00430}{Finland}
\phone[mobile]{+(358)~403~697~874}
%\phone[fixed]{+(358)~403~697~874}
\email{son.trung.to@gmail.com}
%\homepage{www.sonto.com}
\social[github]{SonTrungTo}

\begin{document}
  \makecvtitle

  \section{Education}
  \cventry{2012--2016}{B.Sc in Economics}{Aalto University}{Helsinki}{}%
  {}
  \cventry{2020}{Certificate in FullStack Open 2020}{University Of Helsinki}{Helsinki}{\textit{5/5}}%
  {Solved every exercise in the course}
  \cventry{2021}{Certificate in DevOps 2020 Docker}{University Of Helsinki}{Helsinki}{\textit{3/3}}%
  {Solved every exercise with the highest credits possible}
  \cventry{2021}{Certificate in React Native 2020}{University Of Helsinki}{Helsinki}{}%
  {Solved 12/27 exercises. The app interface is finished. The authentication is being done at the moment.}

  \section{Experience}
  \subsection{Vocational}
  \cventry{2015--2020}{Restaurant worker}{}{Helsinki}{}%
  {}
  \cventry{2019}{Microeconomic student at FDPE}{Aalto University}{Helsinki}{\textit{3/5}}%
  {I passed the course Microeconomic theory 3 at Finnish Doctoral Program in Economics (FDPE)
  while being a restaurant worker at another place.}
  \cventry{2020-present}{FullStack Web Developer}{Freelance}{Helsinki}{}%
  {Within one year, I have solved every exercises in Eloquent Javascript, helped its authors
  corrected some mistakes in the book, familiarized myself with modern web
  development in 15 different projects, notably a game in JavaScript,
  a book store built in MERN (GraphQL), a social media website in MERN (REST)
  and every exercise from the course FullStack Open 2020, DevOps 2020 with Docker
  with an introduction to Kubernetes.
  \\
  Will soon be finshing courses in Kubernetes and Cloud
  development: Amazon Web Service (AWS), Azure and Google Cloud Platform (GCP).}

  \section{Languages}
  \cvitemwithcomment{English}{Fluent}{}
  \cvitemwithcomment{Finnish}{Intermediate}{}
  \cvitemwithcomment{Swedish}{Beginner}{}
  \cvitemwithcomment{Vietnamese}{Mother tongue}{}

  \clearpage

  \section{Computer Skills}
  \cvdoubleitem{Low-end}{C, Linux, VM}{Document}{\LaTeX}
  \cvdoubleitem{Statistics}{Stata, R, Python}{Front-End}{React, Material-UI, Bootstrap, Semantic-UI-React, Typescript}
  \cvdoubleitem{Back-End}{Node, Typescript, MongoDB, Express, PostGreSQL}{Architecture}{RESTful, GraphQL, Flex, Redux, Rethunk}
  \cvdoubleitem{DevOps}{Docker, Kubernetes}{}{}%{Cloud}{AWS}
  \cvdoubleitem{Mobile}{React-Native}{}{}

  \clearpage

  %------ letter -------------------------------------
  \recipient{Company Recruitment Team}{Dream Broker Fullstack Developer\\Helsinki}
  \date{February 8, 2021}
  \opening{Dear Sir or Madam,}
  \closing{Yours faithfully,}
  \enclosure[Attached]{Curriculum Vit\ae{}}
  \makelettertitle

  I am writing this letter to express my interest in joining
  Dream Broker Fullstack Developer.

  I have had background in programming ever since 2016, with my
  first language being the C Programming Language by K \& R. Starting
  from that, and thanks to the Coronavirus, I have had the chance
  to seriously study and make my first steps in being a
  one of the best FullStack Developers you can find in Finland.
  As you can see from my portfolio, I am very well on my way to become
  a better developer. As I am trying to become a more fluent developer on Kubernetes,
  I hope you will give me a chance to grow more as a developer,
  such as skills in working with teammates, communicating with and helping other
  people to succeed!

  Keywords: MERN, TypeScript, Docker, JavaScript, React-Native, Jest

  So due to these details, I am confident that I will be a valuable, diversified
  part of the team and make Dream Broker becomes a better place.

  \makeletterclosing



\end{document}
