\documentclass[a4paper,11pt]{memoir}
\usepackage[affil-it]{authblk}
\usepackage{amsmath,amssymb,amsthm,fancyhdr,enumitem,%
hyperref,microtype}
\usepackage[retainorgcmds]{IEEEtrantools}
\newcommand{\note}[1]{\emph{#1}}
\theoremstyle{plain} \newtheorem{id}{Lemma}
                     \newtheorem{thm}{Theorem}
\theoremstyle{definition} \newtheorem{pr}{Problem}[chapter]
\theoremstyle{remark}\newtheorem*{ab}{Remark}
\newcommand{\idautorefname}{Lemma}
\newcommand{\abautorefname}{Remark}
\newcommand{\thmautorefname}{Theorem}
\newenvironment{solution}%
{\renewcommand{\qedsymbol}{$\blacksquare$}%
\begin{proof}[Solution]}%
{\end{proof}}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[LO,RE]{\textsl{\leftmark}}
\fancyhead[RO,LE]{Page \thepage\ of \thelastpage}
\fancyfoot[C]{Son To}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

\begin{document}

  \title{Solutions to Michael Spivak's Calculus}
  \author{Son To\\
  $<$\href{mailto:son.trung.to@gmail.com}%
  {son.trung.to@gmail.com}$>$}
  \affil{Ravintola Kiltakellari
  \thanks{This document would have never
  been made without the hiring of my employer!
  Thank you!}}
  \date{25th June, 2017}

  \maketitle
  \makeatletter
  \def\cleardoublepage{\clearpage\if@twoside
  \ifodd\c@page\else
    \hbox{}
    \vspace*{\fill}
    \begin{center}
      \doublenote
    \end{center}
    \vspace*{\fill}
    \thispagestyle{empty}
    \newpage
    \if@twocolumn\hbox{}\newpage\fi\fi\fi
}
\newcommand{\mylabel}[2]{#2\def\@currentlabel{#2}\label{#1}}
\def\@endpart{\vfill\newpage
              \if@twoside
                \if@openright
                  \null
                  \thispagestyle{empty}%
%-------------------------------
\vspace*{\fill}%
\begin{quote}%
  \partnote
\end{quote}%
\vspace*{\fill}%
%-------------------------------
                  \newpage
                \fi
              \fi
              \if@tempswa
                \twocolumn
              \fi
}
\newcommand{\partnote}{}
\newcommand{\doublenote}{}
\makeatother

\renewcommand{\doublenote}{This page is
intentionally left blank}
\frontmatter
  \chapter{Preface}
    What is the point of writing a solution manual when
    one, written by the author, has already existed?

    \medskip
    The choice has two personal reasons.

    \medskip
    Reason \#1:
    I was first enrolled in Aalto University School of Business
    back in 2012 as a freshman. Subsequently, I ascertained that
    the teaching of Aalto is really good for business
    students, but I am neither a businessman
    nor an any other type of student: I am a geek
    who loves his freedom of academic pursuits; therefore,
    writing the solution manual is simply the way I satisfy
    myself with one of the legendary books in mathematics.

    Reason \#2:
    I have a long history with the book. Since Calculus
    plays a really important role in Statistics, which
    eventually plays an important role in Economics(%
    and almost every other fields of science), I searched
    intensively for a thorough book that \note{really}
    teaches Calculus without ommitting the details
    back when I was a freshman in 2012, and it turned out that
    Spivak was my choice. However, due to the already
    intensive teaching of my program, I barely had any time
    to read the book properly. Moreover, due to my status
    of not being a native Finnish citizen, I really had
    so many problems both in term of finance and of legality
    to be in Finland because of my staunch determination of not
    wanting to go back to my home country, Vietnam%
    . This further prevents me from reading
    the book in an edifying way. And now after having
    acquainted myself with the basic of \LaTeXe, I really
    want to do as many projects in mathematics as I can,
    and Spivak's Calculus is obviously my first choice.

    \medskip
    Moreover, I really do believe that originality is
    not something that comes from following a particular
    way of doing things but rather a strange, personal journey
    made, written and discovered on your own regardless of
    how silly
    and redundant it might be!
    \flushright
    Vantaa, Finland \\
    25th June,2017.
  \clearpage
  \tableofcontents

\mainmatter
  \renewcommand{\partnote}{
    I held every man a debtor\\
    to his profession\ldots
    \flushright
    Francis Bacon.
  }
  \part{Prologue}
    \chapter{Basic properties of number}
    \input{ch1/ch1}
\end{document}
