\chapter{Numbers of Various Sorts}
\begin{pr} \label{2.1}% 2.1
  Prove the following formula by induction.
  \begin{enumerate}[label=(\roman*)]
    \item \label{2.1:i}
    $1^2+\dots+n^2=\dfrac{n(n+1)(2n+1)}{6}$.
    \item $1^3+\dots+n^3=(1+\dots+n)^2$.
  \end{enumerate}
\end{pr}

\begin{solution} % s2.1
  \begin{enumerate}[label=(\roman*)]
    \item If $n=1$, the equation holds. Suppose the
    equation holds for $n=k$, then for $n=k+1$,
    \begin{IEEEeqnarray*}{lC}
      & 1^2+\dots+k^2+(k+1)^2 \\
    = & \frac{k(k+1)(2k+1)}{6} + (k+1)^2 \\
    = & \frac{(k+1)[k(2k+1)+6(k+1)]}{6}  \\
    = & \frac{(k+1)(2k^2+7k+6)}{6}       \\
    = & \frac{(k+1)(2k^2+4k+3k+6)}{6}    \\
    = & \frac{(k+1)[2k(k+2)+3(k+2)]}{6}  \\
    = & \frac{(k+1)[(k+1)+1][2(k+1)+1]}{6}
    \end{IEEEeqnarray*}
    Then the formula holds for every $n$.
    \item If $n=1$, there is nothing to prove. If
    $n=k$ holds for the equation, then for $n=k+1$,
    \begin{IEEEeqnarray*}{lC}
      & [1+\dots+k+(k+1)]^2 \\
    = & (1+\dots+k)^2 + (k+1)^2 + 2(k+1)(1+\dots+k) \\
    = & 1^3+\dots+k^3 + (k+1)[(k+1)+2\frac{k(k+1)}{2}] \\
    = & 1^3+\dots+k^3 + (k+1)^3
    \end{IEEEeqnarray*}
    This finishes the proof for every $n$.
  \end{enumerate}
\end{solution}

\begin{pr} % 2.2
  Find a formula for
  \begin{enumerate}[label=(\roman*)]
    \item
    $\displaystyle\sum_{i=1}^n (2i-1) = 1+3+5+\dots+(2n-1)$.
    \item $\displaystyle\sum_{i=1}^n (2i-1)^2
    = 1^2 + 3^2 + 5^2 + \dots + (2n - 1)^2$.
  \end{enumerate}
  Hint: What do these expressions have to do with
  $1 + 2 + 3 + \dots + 2n$ and $1^2 + 2^2 + 3^2 + \dots
  + (2n)^2$?
\end{pr}

\begin{solution} % s2.2
  \begin{enumerate}[label=(\roman*)]
    \item Remind that $1+\dots+2n=n(2n+1)$ and
    that $2 + \dots + 2n = 2 \cdot \dfrac{n(n+1)}{2} = n(n+1)$.
    Hence,
    \begin{equation*}
      \sum_{i=1}^n (2i - 1) = n(2n+1) - n(n+1) = n^2
    \end{equation*}
    \item Using \autoref{2.1}\ref{2.1:i}, we easily
    derive that $\displaystyle
    \sum_{i=1}^{2n} i^2 = \dfrac{n(2n+1)(4n+1)}{3}$
    and $\displaystyle
    \sum_{i=1}^n (2i)^2 = \dfrac{2n(n+1)(2n+1)}{3}$.
    Therefore,
    \begin{equation*}
      \sum_{i=1}^n (2i - 1)^2 = \sum_{i=1}^{2n} i^2
      - \sum_{i=1}^n (2i)^2
      = \frac{n(4n^2 - 1)}{3}
    \end{equation*}
  \end{enumerate}
\end{solution}

\begin{pr} \label{2.3} % 2.3
  If $0 \leq k \leq n$, the ``binomial coefficient''
  $\displaystyle\binom{n}{k}$ is defined by
  $\displaystyle\binom{n}{k} = \dfrac{n!}{k!(n-k)!}
  = \dfrac{n(n-1)\cdots(n-k+1)}{k!}$, if $k\neq0,n$ \\
  $\displaystyle\binom{n}{0} = \binom{n}{n} = 1$.
  (This becomes a special case of the first formula
  if we define $0! = 1$.)
  \begin{enumerate}[label=(\alph*)]
    \item \label{2.3:a}
    Prove that
    \begin{equation*}
      \binom{n+1}{k} = \binom{n}{k-1} + \binom{n}{k}.
    \end{equation*}
    (The proof does not require an induction argument.)

    \medskip
    This relation gives rise to the following configuration,
    known as ``Pascal's triangle''---a number not on one of the
    sides is the sum of two numbers above it; the binomial
    coefficient $\displaystyle\binom{n}{k}$ is the
    $(k+1)$st number in the $(n+1)$st row.
    \par
    \begin{center} \label{PascalTriangle}
      \begin{tikzpicture}
        \foreach \n in {0,...,5}{
          \foreach \k in {0,...,\n}{
            \node at (\k - \n/2, -\n){$\binomialCoefficient{\n}{\k}$};
          }
        }
      \end{tikzpicture}
    \end{center}
    \item Notice that all numbers in Pascal's triangle are
    natural numbers. Use part \ref{2.3:a} to prove by
    induction that $\displaystyle\binom{n}{k}$ is always
    a natural number. (Your entire proof by induction will,
    in a sense, be summed up in a glance by Pascal's
    triangle.)
    \item Give another proof that $\displaystyle\binom{n}{k}$
    is a natural number by showing that
    $\displaystyle\binom{n}{k}$ is the number of sets of
    exactly $k$ integers each chosen from $1,\dots,n$.
    \item Prove the ``binomial theorem'': If $a$ and $b$
    are any numbers and $n$ is a natural number, then
    \begin{IEEEeqnarray*}{rCl}
      (a+b)^n & = & a^n + \binom{n}{1}a^{n-1}b
      + \binom{n}{2}a^{n-2}b^2+\cdots+\binom{n}{n-1}ab^{n-1}
      + b^n \\
              & = & \sum_{j=0}^n \binom{n}{j}a^{n-j}b^j.
    \end{IEEEeqnarray*}
    \item Prove that
    \begin{enumerate}[label=(\roman*)]
      \item \label{2.3:ei}
      $\displaystyle
      \sum_{j=0}^n \binom{n}{j}
      = \binom{n}{0} + \cdots + \binom{n}{n}
      = 2^n$.
      \item \label{2.3:eii}
      $\displaystyle
      \sum_{j=0}^n (-1)^j \binom{n}{j}
      = \binom{n}{0} - \binom{n}{1} + \cdots \pm \binom{n}{n}
      = 0$.
      \item $\displaystyle
      \sum_{l\text{ odd}} \binom{n}{l}
      = \binom{n}{1} + \binom{n}{3} + \cdots
      = 2^{n - 1}$.
      \item $\displaystyle
      \sum_{l\text{ even}} \binom{n}{l}
      = \binom{n}{0} + \binom{n}{2} + \cdots
      = 2^{n - 1}$.
    \end{enumerate}
  \end{enumerate}
\end{pr}

\begin{solution} % s2.3
  \begin{enumerate}[label=(\alph*)]
    \item Starting from the left-hand side,
    \begin{IEEEeqnarray*}{rCl}
      \binom{n + 1}{k} & = &
      \frac{n!(n - k + 1 + k)}{k!(n - k + 1)!} \\
                       & = &
      \frac{n!(n - k + 1)}{k!(n - k + 1)!}
    + \frac{n!k}{k!(n - k + 1)!}\\
                       & = &
      \frac{n!}{k!(n - k)!}
    + \frac{n!}{(k - 1)![n - (k - 1)]!} \\
                       & = &
      \binom{n}{k} + \binom{n}{k - 1}
    \end{IEEEeqnarray*}
    \item It is sufficient to prove that $\displaystyle
    \binom{n}{k}$ is a natural number for all
    $1 \leq k \leq (n - 1)$. If $n = 1$, then
    \begin{equation*}
      \binom{2}{1} = \binom{1}{0} + \binom{1}{1} = 2
    \end{equation*}
    Suppose that $\displaystyle\binom{n}{k}$ is natural
    number for any $n$ and $1 \leq k \leq n - 1$.
    Then for any $1 \leq k \leq n$, $\displaystyle
    \binom{n + 1}{k}$ is the sum of two natural numbers,
    and therefore it must be a natural number.
    \item It is sufficient to prove for the case
    $0 < k \leq n$.
    If $n=1$, the claim is trivial. Suppose that
    $\displaystyle\binom{n}{k}$ is the number of sets
    of $k$ integers each chosen from $1,\dots,n$; then
    $\displaystyle\binom{n + 1}{k}$ must include
    $\displaystyle\binom{n}{k}$ sets of $k$ integers
    \note{without} the newly added element and a number
    of sets of $k$ integers \note{with} the newly added
    element. The latter is exactly $\displaystyle
    \binom{n}{k - 1}$ and is a natural number by assumption.
    Thereby, $\displaystyle\binom{n+1}{k}$ must be
    a natural number.
    \item We prove by induction on $n$. If $n=1$, there
    is nothing to prove. Suppose the binomial theorem holds
    for $n$; then for $n+1$,
    \begin{IEEEeqnarray*}{rCl}
      (a+b)^n(a+b) & = &
      \sum_{j=0}^n \binom{n}{j} a^{n-j}b^j(a + b) \\
                   & = &
      \sum_{j=0}^n \binom{n}{j} a^{n+1-j}b^j
    + \sum_{j=0}^n \binom{n}{j} a^{n-j}b^{j+1}    \\
                   & = &
      a^{n + 1} + b^{n + 1}
    + \sum_{j=1}^n \binom{n}{j} a^{n+1-j}b^j      \\
                   & + &
      \sum_{j=1}^n \binom{n}{j-1} a^{n+1-j}b^j    \\
                   & = &
      \sum_{j=1}^n \binom{n+1}{j} a^{n+1-j}b^j
    + a^{n+1} + b^{n+1}                           \\
                   & = &
      \sum_{j=0}^{n+1} \binom{n+1}{j} a^{n+1-j}b^j
    \end{IEEEeqnarray*}
    which completes the proof.
    \item This part relies heavily on
    the binomial theorem from the above.
    \begin{enumerate}[label=(\roman*)]
      \item This is directly from the above: Applying
      the binomial theorem for $a=b=1$ yields the result.
      \item Let $a=1$ and $b=-1$ yield the result.
      \item Applying \ref{2.3:ei} $+$ \ref{2.3:eii},
      we derive that for $l$ even,
      \begin{equation*}
        \sum_{l\text{ even}} \binom{n}{l} = 2^{n - 1}
      \end{equation*}
      Thereby, $\displaystyle
      \sum_{l\text{ odd}} \binom{n}{l} = 2^n - 2^{n - 1}
      = 2^{n - 1}$.
      \item See the above.
    \end{enumerate}
    One thing to note: Both of the previous parts do not
    have a final term expressed in their sum due to the
    dependence of value $n$ (if $n$ is even or odd).
  \end{enumerate}
\end{solution}

\begin{pr} \label{2.4} % 2.4
  \begin{enumerate}[label=(\alph*)]
    \item \label{2.4:a}
    Prove that
    \begin{equation*}
      \sum_{k=0}^l \binom{n}{k} \binom{m}{l-k}
      = \binom{n+m}{l}.
    \end{equation*}
    Hint: Apply the binomial theorem to $(1+x)^n(1+x)^m$.
    \item \label{2.4:b}
    Prove that
    \begin{equation*}
      \sum_{k=0}^n \binom{n}{k}^2 = \binom{2n}{n}.
    \end{equation*}
  \end{enumerate}
\end{pr}

\begin{solution} % 2.4 solved
  \begin{enumerate}[label=(\alph*)]
    \item Remind that $(1+x)^n(1+x)^m = (1+x)^{n+m}$. Hence,
    \begin{equation*}
      \sum_{k=0}^n \binom{n}{k}x^k \cdot
      \sum_{j=0}^m \binom{m}{j}x^j
      = \sum_{l=0}^{n+m} \binom{n+m}{l}x^l
    \end{equation*}
    Observing that each term of $x^l$ is
    \begin{equation*}
      \sum_{k=0}^l \binom{n}{k}\binom{m}{l-k}
    \end{equation*}
    for every $k$ and $j$ such that $j = l - k$.
    \item From \ref{2.4:a}, let $m = l = n$ and observe
    that for all $0\leq k\leq n$,
    \begin{equation*}
      \binom{n}{k} = \binom{n}{n - k}
    \end{equation*}
    since $\dfrac{n!}{k!(n-k)!} = \dfrac{n!}{(n-k)!k!}$.
    Hence,
    $\displaystyle\sum_{k=0}^n \binom{n}{k}^2 = \binom{2n}{n}$.
  \end{enumerate}
\end{solution}

\begin{pr} \label{2.5} % 2.5
  \begin{enumerate}[label=(\alph*)]
    \item \label{2.5:a}
    Prove by induction on $n$ that
    \begin{equation*}
      1 + r + r^2 + \cdots + r^n = \frac{1-r^{n+1}}{1-r}
    \end{equation*}
    if $r\neq1$ (if $r=1$, evaluating the sum certainly
    presents no problem).
    \item \label{2.5:b}
    Derive this result by setting $S = 1 + r + \cdots + r^n$,
    multiplying this equation by $r$, and solving the
    two equations for $S$.
  \end{enumerate}
\end{pr}

\begin{solution} % 2.5 solved
  \begin{enumerate}[label=(\alph*)]
    \item If $n=1$, then the formula immediately holds. Suppose
    now that it holds for $n$, then for $n+1$,
    \begin{IEEEeqnarray*}{rCl}
      1 + r + \cdots + r^n + r^{n+1}
    & = & \frac{1 - r^{n+1}}{1-r} + r^{n+1} \\
    & = & \frac{1 - r^{n + 2}}{1 - r}
  \end{IEEEeqnarray*}
  which completes the proof.
    \item Let
    \begin{equation*}
      S = 1 + r + r^2 + \cdots + r^n
    \end{equation*}
    then
    \begin{equation*}
      rS = r + r^2 + r^3 + \cdots + r^{n+1}
    \end{equation*}
    Solving for $S$, we easily obtain
    \begin{equation*}
      S = \frac{1 - r^{n+1}}{1 - r}
    \end{equation*}
  \end{enumerate}
\end{solution}

\begin{pr} \label{2.6} % 2.6
  The formula for $1^2 + \cdots + n^2$ may be derived as
  follows. We begin with the formula
  \begin{equation*}
    (k+1)^3 - k^3 = 3k^2 + 3k + 1.
  \end{equation*}
  Writing this formula for $k=1,\dots,n$ and adding,
  we obtain

  \bigskip
  \begin{IEEEeqnarray*}{rCl}
    2^3 - 1^3 & = & 3 \cdot 1^2 + 3 \cdot 1 + 1 \\
    3^3 - 2^3 & = & 3 \cdot 2^2 + 3 \cdot 2 + 1 \\
    \vdots                                      \\
    (n + 1)^3 - n^3 & = & 3 \cdot n^2 + 3 \cdot n + 1 \\
    \hline                                            \\
    (n + 1)^3 - 1 & = & 3[1^2 + \cdots + n^2]
    + 3[1 + \cdots + n] + n.
  \end{IEEEeqnarray*}

  \bigskip
  Thus we can find
  $\displaystyle \sum_{k=1}^n k^2$ if we already know
  $\displaystyle \sum_{k=1}^n k$ (which could have been
  found in a similar way). Use this method to find
  \begin{enumerate}[label=(\roman*)]
    \item $1^3 + \cdots + n^3$.
    \item $1^4 + \cdots + n^4$.
    \item $\displaystyle
    \frac{1}{1\cdot2} + \frac{1}{2\cdot3} + \cdots
    + \frac{1}{n(n + 1)}$.
    \item $\displaystyle
    \frac{3}{1^2\cdot2^2} + \frac{5}{2^2\cdot3^2} + \cdots
    + \frac{2n + 1}{n^2(n + 1)^2}$.
  \end{enumerate}
\end{pr}

\begin{solution} % 2.6 solved
  \begin{enumerate}[label=(\roman*)]
    \item We easily derive that
    \begin{equation*}
      (k+1)^4 - k^4 = 4k^3 + 6k^2 + 4k + 1
    \end{equation*}
    Hence,
    \begin{IEEEeqnarray*}{rCl}
      2^4 - 1^4 &=& 4\cdot1^3 + 6\cdot1^2 + 4\cdot1 + 1 \\
      3^4 - 2^4 &=& 4\cdot2^3 + 6\cdot2^2 + 4\cdot2 + 1 \\
      \vdots                                            \\
      (n + 1)^4 - n^4 &=& 4\cdot n^3 + 6 \cdot n^2
      + 4 \cdot n + 1                                   \\
      \hline                                            \\
      (n + 1)^4 - 1 &=& 4[1^3 + 2^3 + \cdots + n^3]     \\
      & + & 6[1^2 + 2^2 + \cdots + n^2] + 4[1 + 2 + \cdots + n]
      + n
    \end{IEEEeqnarray*}
    It is easily derivable that
    \begin{equation*}
      1^3 + \cdots + n^3 = \frac{1}{4}n^2(n + 1)^2
    \end{equation*}
    \item The easiest way to calculate
    $(k + 1)^5 - k^5$ is to use the Pascal triangle from
    page \pageref{PascalTriangle}: We derive the result
    \begin{equation*}
      (k + 1)^5 - k^5 = 5k^4 + 10k^3 + 10k^2 + 5k + 1
    \end{equation*}
    A similar step from above shows that
    \begin{IEEEeqnarray*}{rCl}
      (n + 1)^5 - 1 & = & 5[1^4 + \cdots + n^4]
      + 10[1^3 + \cdots + n^3] \\
                      & + & 10[1^2 + \cdots + n^2]
      + 5[1 + \cdots + n] + n
    \end{IEEEeqnarray*}
    We derive from the available results,
    \begin{equation*}
      1^4 + 2^4 + \cdots + n^4 = \frac{1}{30}
      n(n+1)(2n+1)(3n^2 + 3n - 1)
    \end{equation*}
    \item Observe that
    \begin{equation*}
      \frac{1}{k} - \frac{1}{k + 1} = \frac{1}{k(k + 1)}
    \end{equation*}
    Henceforth,
    \begin{IEEEeqnarray*}{rCl}
      1 - \frac{1}{2} &=& \frac{1}{1\cdot2} \\
      \frac{1}{2} - \frac{1}{3} &=& \frac{1}{2\cdot3} \\
      \vdots                                          \\
      \frac{1}{n} - \frac{1}{n + 1}
      &=& \frac{1}{n\cdot(n+1)}                       \\
      \hline                                          \\
      1 - \frac{1}{n + 1} & = &
      \frac{1}{1\cdot2} + \frac{1}{2\cdot3} + \cdots
      + \frac{1}{n(n + 1)}                            \\
      \frac{1}{1\cdot2} + \frac{1}{2\cdot3} + \cdots
      + \frac{1}{n(n + 1)}& = & \frac{n}{n + 1}
    \end{IEEEeqnarray*}
    \item See that
    \begin{equation*}
      \frac{1}{k^2} - \frac{1}{(k+1)^2}
      = \frac{2k + 1}{k^2(k + 1)^2}
    \end{equation*}
    Henceforth,
    \begin{IEEEeqnarray*}{rCl}
      1 - \frac{1}{2^2} &=& \frac{3}{1^2\cdot2^2} \\
      \frac{1}{2^2} - \frac{1}{3^2} &=& \frac{5}{2^2\cdot3^2} \\
      \vdots \\
      \frac{1}{n^2} - \frac{1}{(n+1)^2} &=&
      \frac{2n + 1}{n^2(n + 1)^2}                  \\
      \hline                                       \\
      \frac{3}{1^2\cdot2^2} + \frac{5}{2^2\cdot3^2}
      + \cdots + \frac{2n + 1}{n^2(n + 1)^2}
      & = & \frac{n(n+2)}{(n+1)^2}
    \end{IEEEeqnarray*}
  \end{enumerate}
\end{solution}

\begin{pr} \label{2.7}% 2.7
  Use the method of \autoref{2.6} to show that $\displaystyle
  \sum_{k=1}^n k^p$ can always be written in the form
  \begin{equation*}
    \frac{n^{p+1}}{p+1} + An^{p} + Bn^{p-1}
    + Cn^{p-2} + \cdots .
  \end{equation*}
  (The first 10 such expressions are
  \begin{IEEEeqnarray*}{rCCCCCCCCCCCCCCl}
    \sum_{k=1}^n k & = &
    \frac{1}{2}n^2 &+& \frac{1}{2}n \\
    \sum_{k=1}^n k^2 &=&
    \frac{1}{3}n^3 &+& \frac{1}{2}n^2
    &+& \frac{1}{6}n                                     \\
    \sum_{k=1}^n k^3 &=&
    \frac{1}{4}n^4 &+& \frac{1}{2}n^3
    &+& \frac{1}{4}n^2                                   \\
    \sum_{k=1}^n k^4 &=&
    \frac{1}{5}n^5 &+& \frac{1}{2}n^4
    &+& \frac{1}{3}n^3 &-& \frac{1}{30}n                   \\
    \sum_{k=1}^n k^5 &=&
    \frac{1}{6}n^6 &+& \frac{1}{2}n^5
    &+& \frac{5}{12}n^4 &-& \frac{1}{12}n^2                \\
    \sum_{k=1}^n k^6 &=&
    \frac{1}{7}n^7 &+& \frac{1}{2}n^6
    &+& \frac{1}{2}n^5 &-& \frac{1}{6}n^3 &+& \frac{1}{42}n  \\
    \sum_{k=1}^n k^7 &=&
    \frac{1}{8}n^8 &+& \frac{1}{2}n^7
    &+& \frac{7}{12}n^6 &-& \frac{7}{24}n^4
    &+& \frac{1}{12}n^2 \\
    \sum_{k=1}^n k^8 &=&
    \frac{1}{9}n^9 &+& \frac{1}{2}n^8
    &+& \frac{2}{3}n^7 &-& \frac{7}{15}n^5 &+& \frac{2}{9}n^3
    &-& \frac{1}{30}n                                       \\
    \sum_{k=1}^n k^9 &=&
    \frac{1}{10}n^{10}
    &+& \frac{1}{2}n^9 &+& \frac{3}{4}n^8
    &-& \frac{7}{10}n^6 &+& \frac{1}{2}n^4
    &-& \frac{3}{20}n^2  \\
    \sum_{k=1}^n k^{10} &=&
    \frac{1}{11}n^{11} &+& \frac{1}{2}n^{10}
    &+& \frac{5}{6}n^9 &-& 1n^7 &+& 1n^5 &-& \frac{1}{2}n^3
    &+& \frac{5}{66}n.
  \end{IEEEeqnarray*}
  Notice that the coefficients in the second column are
  always $\dfrac{1}{2}$, and that after the third column
  the powers of $n$ with nonzero coefficients decrease
  by $2$ until $n$ or $n^2$ is reached. The coefficients
  in all but the first two columns seem to be rather
  haphazard, but there is actually is some sort of pattern;
  finding it may be regarded as a super-perspicacity test.
  See Problem 27.17 for the complete story.)
\end{pr}

\begin{solution} % 2.7 solved
  We prove by complete induction on $p$. Know that
  \begin{equation*}
    (k+1)^{p+2} - k^{p+2}
  = \sum_{j=2}^{p} \binom{p+2}{j}k^j
  + (p+2)k^{p+2} + (p+2)k + 1
  \end{equation*}
  If $p=1$, it is obvious. Suppose the expression holds
  for $1,\dots,p$, then for $p+1$,
  using the known method presented above, we easily obtain
  \begin{equation*}
    (n+1)^{p+2} - 1
  = \sum_{j=2}^{p} \binom{p+2}{j} \sum_{k=1}^n k^j
  + (p+2)\sum_{k=1}^n k^{p+1} + (p+2)\sum_{k=1}^n k + n
  \end{equation*}
  Notice that the left-hand side highest power of $n$ is
  $p+2$ while that on the right is $p+1$ by assumption.
  Dividing both sides by $p+2$ and solve for
  $\sum_{k=1}^n k^{p+1}$, we have
  \begin{equation*}
    \sum_{k=1}^n k^{p+1}
  = \frac{n^{p+2}}{p+2} + An^{p+1} + Bn^p + \cdots
  \end{equation*}
  for some number $A$, $B$.
\end{solution}

\begin{pr} % 2.8
  Prove that every natural number is either even or odd.
\end{pr}

\begin{solution} % 2.8 solved
  Suppose that $B$
  is the set of all natural numbers that is neither even
  nor odd. Suppose that $B\neq\emptyset$. Obviously,
  $1\notin B$ since $1$ is an odd number. If $k \notin B$,
  then $k$ is either even or odd. Then $k + 1$ is either
  odd or even, and therefore $(k+1) \notin B$. Henceforth,
  $B = \emptyset$, contradicting assumption.
\end{solution}

\begin{pr} % 2.9
  Prove that if a set $A$ of natural numbers contains $n_0$
  and contains $k+1$ whenever it contains $k$, then $A$
  contains all natural numbers $\geq n_0$.
\end{pr}

\begin{solution} % 2.9 solved
  Obivously, $n_0 \in A$. Suppose that $(n_0 + k - 1) \in A$.
  By assumption, $(n_0 + k) \in A$. Hence, $A$ contains all
  natural numbers $\geq n_0$.
\end{solution}

\begin{pr} % 2.10
  Prove the principle of mathematical induction from the
  well-ordering principle.
\end{pr}

\begin{solution} \label{2.10} % 2.10 solved
  We shall prove the theorem by contradiction,
  \begin{thm}[Principle of mathematical induction]
    If $A$ is the set of natural numbers and
    \begin{enumerate}[label=(\arabic*)]
      \item \label{2.10:1}
      $1$ is in $A$
      \item \label{2.10:2}
      $k+1$ is in $A$ wherever $k$ is in $A$,
    \end{enumerate}
    then $A$ is the set of all natural numbers.
  \end{thm}
  Let $B\neq\emptyset$
  be the set of all natural numbers \note{not}
  in $A$. By the well-ordering principle, $B$ has a least
  member $k$. By construction, $k \notin A$. By property
  \ref{2.10:2}, $(k - 1) \notin A$, which means that
  $(k - 1) \in B$, but this contradicts the fact that
  $k$ is the least member in $B$.
\end{solution}

\begin{pr} % 2.11
  Prove the principle of complete induction from the ordinary
  principle of induction. Hint: If $A$ contains $1$ and $A$
  contains $n + 1$ whenever it contains $1,\dots,n$,
  consider the set $B$ of all $k$ such that $1,\dots,k$
  are all in $A$.
\end{pr}

\begin{solution} % 2.11 solved
  We want to prove the following theorem,
  \begin{thm}[Principle of complete induction]
    If $A$ is the set of natural numbers and
    \begin{enumerate}[label=(\arabic*)]
      \item $1$ is in $A$
      \item $n+1$ is in $A$ if $1,\dots,n$ is in $A$
    \end{enumerate}
    then $A$ is the set of all natural numbers.
  \end{thm}
  Let $B$ be the set of all $k$ such that
  $1,2,3,\dots,k$ are all in $A$. Obviously, $B \subseteq A$.
  Conversely, $A \subseteq B$ because if not,
  then $1,\dots,k$ are not all in $A$ which implies
  $1 \notin A$.
  Hence,
  $A = B\neq\emptyset$
  since $1\in A$. We see that $B$ satisfies:
  \begin{enumerate}[label=(\arabic*)]
    \item $1$ is in $B$
    \item $k+1$ is in $B$ whenever $k$ is in $B$. Otherwise,
    $(k+1) \notin A$, which implies $1,\dots,k$
    are not in $A$,
    which implies $k \notin B$.
  \end{enumerate}
  By principle of mathematical induction, $B$ is the set of
  all natural numbers, which means $A$ is the same.
\end{solution}

\begin{pr} \label{2.12}% 2.12
  \begin{enumerate}[label=(\alph*)]
    \item If $a$ is rational and $b$ is irrational, is
    $a + b$ necessarily irrational? What if $a$ and $b$
    are both irrational?
    \item If $a$ is rational and $b$ is irrational,
    is $ab$ necessarily irrational? (Careful!)
    \item Is there a number $a$ such that $a^2$ is irrational,
    but $a^4$ is rational?
    \item Are there two irrational numbers whose sum and
    product are both rational?
  \end{enumerate}
\end{pr}

\begin{solution} % 2.12 solved
  \begin{enumerate}[label=(\alph*)]
    \item If $a+b$ were rational then
    $b = (a+b) - a$ would be rational! Hence,
    $a+b$ is necessarily irrational. However,
    if $a$ and $b$ are irrational, then let $b = r - a$ for
    any rational $r$, then $a+b$ is rational.
    \item $ab$ is not necessarily irrational for the case
    when $a = 0$ and $b = \sqrt{2}$. However, if $a \neq 0$,
    then if $ab$ were rational, then $\dfrac{ab}{a} = b$
    would be rational. Hence, $ab$ must be irrational.
    \item Let $a = \sqrt{\sqrt{2}}$: $a^2 = \sqrt{2}$, but
    $a^4 = 2$.
    \item Let $a = -\sqrt{2}$ and $b = \sqrt{2}$. Then
    both $a+b$ and $ab$ are rational even though $a$
    and $b$ are irrational.
  \end{enumerate}
\end{solution}

\begin{pr} \label{2.13} % 2.13
  \begin{enumerate}[label=(\alph*)]
    \item Prove that $\sqrt{3},\sqrt{5},$ and $\sqrt{6}$ are
    irrational. Hint: To treat $\sqrt{3}$, for example, use
    the fact that every integer is of the form $3n$ or
    $3n + 1$ or $3n + 2$. Why does this proof not work for
    $\sqrt{4}$?
    \item Prove that $\sqrt[3]{2}$ and $\sqrt[3]{3}$ are
    irrational.
  \end{enumerate}
\end{pr}

\begin{solution} % 2.13 solved
  \begin{enumerate}[label=(\alph*)]
    \item Since every number is written in the form of
    either $3n$, $3n+1$ or $3n+2$ for some natural $n$, then
    \begin{IEEEeqnarray*}{rClCl}
      (3n+1)^2  &=& 9n^2+6n+1 &=& 3(3n^2 + 2n) + 1 \\
      (3n+2)^2  &=& 9n^2+12n+4 &=& 3(3n^2 + 4n + 1) + 1
    \end{IEEEeqnarray*}
    This implies that if a squared integer is divisible by $3$,
    then the integer is divisible by $3$.
    Suppose now that $\sqrt{3}$ were rational. Then there
    would be
    a pair of integer $p$ and $q$ with no common divisor such
    that
    \begin{equation*}
      \sqrt{3} = \frac{p}{q}
    \end{equation*}
    This implies that $p^2 = 3 q^2$. Therefore, there exist
    a natural $k$ such that $p = 3 k$, which implies
    \begin{equation*}
      p^2=9k^2=3q^2
    \end{equation*}
    which means that $q^2 = 3 k^2$. Henceforth, $q = 3m$
    for some natural $m$, but these imply that $p$ and $q$
    have a common divisor: A contradiction.
    Similar for $\sqrt{5}$, we consider
    \begin{IEEEeqnarray*}{rClCl}
      (5n+1)^2 &=& 25n^2 + 10n + 1 &=& 5(5n^2 + 2n) + 1\\
      (5n+2)^2 &=& 25n^2 + 20n + 4 &=& 5(5n^2 + 4n) + 4\\
      (5n+3)^2 &=& 25n^2 + 30n + 9 &=& 5(5n^2 + 6n + 1) + 4\\
      (5n+4)^2 &=& 25n^2 + 40n + 16 &=&
      5(5n^2 + 8n + 3) + 1
    \end{IEEEeqnarray*}
    We see that the very same method of proof is applicable
    for $\sqrt{5}$ and $\sqrt{6}$: If $k^2$  is divisible
    by either $5$ or $6$, then $k$ must be divisible by
    $5$ or $6$, respectively. Hence, we easily conclude
    that $\sqrt{5}$ and $\sqrt{6}$ are irrational.
    \par
    Now we cannot use this method of proof for $\sqrt{4}$
    since the statement \note{if $k^2$ is divisible by $4$,
    then $k$ is divisible by $4$} is false by letting $k=2$.
    \item Let us first consider
    \begin{IEEEeqnarray*}{rClCl}
      (2n + 1)^3 &=& 8n^3 + 12n^2 + 6n + 1 &=& 2(4n^3
      + 6n^2 + 3n) + 1
    \end{IEEEeqnarray*}
    We conclude that if $k^3$ is divisible by $2$, then
    $k$ is divisible by $2$ for any natural $k$. Suppose
    $\sqrt[3]{2}$ were rational, then there would be
    integers $p$ and $q$ with no common divisor such that
    \begin{equation*}
      \sqrt[3]{2} = \frac{p}{q}
    \end{equation*}
    then $p^3 = 2 q^3$: $p$ is divisible by $2$,
    and hence $4k^3 = q^3$ for some $k$: $q$ is divisible by $2$:
    A contradiction since both have common divisor. We
    conclude that $\sqrt[3]{2}$ is irrational.
    Similarly,
    \begin{IEEEeqnarray*}{rClCl}
      (3n+1)^3 &=& 27n^3 + 27n^2 + 9n + 1 &=&
      3(9n^3 + 9n^2 + 3n) + 1                 \\
      (3n+2)^3 &=& 27n^3 + 54n^2 + 36n^2 + 8 &=&
      3(9n^3 + 18n^2 + 12n^2 + 2) + 2
    \end{IEEEeqnarray*}
    Hence, for any natural $k$ if $k^3$ is divisible by $3$,
    then $k$ is divisible by $3$. The very same method as above
    is used to prove that $\sqrt[3]{3}$ is irrational.
  \end{enumerate}
\end{solution}

\begin{pr} % 2.14
  Prove that
  \begin{enumerate}[label=(\alph*)]
    \item $\sqrt{2} + \sqrt{6}$ is irrational.
    \item $\sqrt{2} + \sqrt{3}$ is irrational.
  \end{enumerate}
\end{pr}

\begin{solution} % 2.14 solved
  \begin{enumerate}[label=(\alph*)]
    \item Suppose $\sqrt{2} + \sqrt{6}$ is rational. Then
    $(\sqrt{2} + \sqrt{6})^2 = 8 + 4\sqrt{3}$ must be rational.
    Hence, $4\sqrt{3}= 8 + 4\sqrt{3} - 8$ must be rational:
    A contradiction by since $4\neq0$ and $\sqrt{3}$ is
    irrational.
    \item Suppose that $\sqrt{2} + \sqrt{3}$ is rational.
    Then $5 + 2\sqrt{6}$ is rational, which implies
    $2\sqrt{6} = 5 + 2\sqrt{6} - 5$ is rational: A contradiction
    similar to the above.
  \end{enumerate}
\end{solution}

\begin{pr} % 2.15
  \begin{enumerate}[label=(\alph*)]
    \item Prove that if $x = p + \sqrt{q}$ where $p$ and $q$
    are rational, and $m$ is a natural number, then
    $x^m = a + b\sqrt{q}$ for some rational $a$ and $b$.
    \item Prove also that $(p - \sqrt{q})^m = a - b\sqrt{q}$.
  \end{enumerate}
\end{pr}

\begin{solution} % 2.15 solved
  \begin{enumerate}[label=(\alph*)]
    \item Proof is by induction. Let $m=1$, the statement
    holds. Suppose the statement holds for $m$, then for
    $m + 1$,
    \begin{IEEEeqnarray*}{rCl}
      x^{m+1} & = & (a + b\sqrt{q})(p + \sqrt{q}) \\
              & = & (ap + bq) + (a + bp)\sqrt{q}
    \end{IEEEeqnarray*}
    The conclusion follows.
    \item The proof is exactly the same as above except
    now that $x = p - \sqrt{q}$. Hence, for $m + 1$,
    \begin{IEEEeqnarray*}{rCl}
      x^{m+1} & = & (a - b\sqrt{q})(p - \sqrt{q}) \\
              & = & (ap + bq) - (a + bp)\sqrt{q}
    \end{IEEEeqnarray*}
  \end{enumerate}
\end{solution}

\begin{pr} % 2.16
  \begin{enumerate}[label=(\alph*)]
    \item Prove that if $m$ and $n$ are natural numbers
    and $\dfrac{m^2}{n^2} < 2$, then
    $\dfrac{(m + 2n)^2}{(m + n)^2} > 2$; show, moreover, that
    \begin{equation*}
      \frac{(m + 2n)^2}{(m + n)^2} - 2 < 2 - \frac{m^2}{n^2}
    \end{equation*}
    \item Prove the same results with all inequality signs
    reversed.
    \item Prove that if $\dfrac{m}{n} < \sqrt{2}$, then there
    is another rational number $\dfrac{m'}{n'}$ with
    $\dfrac{m}{n} < \dfrac{m'}{n'} < \sqrt{2}$.
  \end{enumerate}
\end{pr}

\begin{solution} % 2.16 solved
  \begin{enumerate}[label=(\alph*)]
    \item We first observe from $m^2/n^2 < 2$,
    \begin{equation*}
      (m + n)^2 < 3n^2 + 2nm
    \end{equation*}
    And from here,
    \begin{IEEEeqnarray*}{rCl}
      \frac{(m+2n)^2}{(m+n)^2} & = &
      \frac{(m+n)^2 + n^2 + 2n(m+n)}{(m+n)^2} \\
                               & = &
      1 + \frac{3n^2 + 2nm}{(n+m)^2}          \\
                               & > &
      1 + 1                                   \\
                              & = &
      2
    \end{IEEEeqnarray*}
    Furthermore,
    \begin{IEEEeqnarray*}{rCl}
      \frac{(m+2n)^2}{(m+n)^2} - 2 & = &
      \frac{-(m+n)^2 + n^2 + 2n(m+n)}{(m+n)^2}  \\
                                   & = &
      \frac{2n^2 - m^2}{(m+n)^2}                \\
                                   & < &
      \frac{2n^2 - m^2}{n^2}                    \\
                                   & = &
      2 - \frac{m^2}{n^2}
    \end{IEEEeqnarray*}
    \item Applying the exact method from the above, we
    see that if $m^2/n^2 > 2$, then
    $\dfrac{(m+2n)^2}{(m+n)^2} < 2$. As for the last inequality,
    note from the third line above: since $2n^2 - m^2 < 0$,
    the inequality sign is reversed. Therefore,
    $\dfrac{(m+2n)^2}{(m+n)^2} - 2 > 2 - \dfrac{m^2}{n^2}$.
    \item Let $m' = 2n^2 - m^2$ and $n' = (m+n)^2$, we obtain
    \begin{equation*}
      \frac{m^2}{n^2} < \frac{m'^2}{n'^2} < 2
    \end{equation*}
    Hence, $\dfrac{m}{n} < \dfrac{m'}{n'} < \sqrt{2}$.
  \end{enumerate}
\end{solution}

\begin{pr}[*] \label{2.17} % 2.17
  It seems likely that $\sqrt{n}$ is irrational whenever
  the natural number $n$ is not the square of another
  natural number. Although the method of \autoref{2.13}
  may actually be used to treat any particular case, it is
  not clear in advance that it will always work, and a proof
  for the general case requires some extra information.
  A natural number $p$ is called \boldText{prime number} if
  it is impossible to write $p = ab$ for natural numbers
  $a$ and $b$ unless one of these is $p$, and the other $1$;
  for convenience we also agree that $1$ is \note{not}
  a prime number. The first few prime numbers are
  $2,3,5,7,11,13,17,19$. If $n > 1$ is not a prime, then
  $n = ab$, with $a$ and $b$ both $< n$; if either $a$ or
  $b$ is not a prime it can be factored similarly; continuing
  in this way proves that we can write $n$ as a product of
  primes. For example, $28 = 4 \cdot 7 = 2\cdot2\cdot7$.
  \begin{enumerate}[label=(\alph*)]
    \item \label{2.17:a}
    Turn this argument into a rigorous proof by
    complete induction.
  \end{enumerate}
  A fundamental theorem about integers, which we will not
  prove here, states that this factorization is unique,
  except for the order of the factors. Thus, for example,
  $28$ can never be written as a product of primes one of
  which is $3$, nor can it be written in a way that involves
  $2$ only once (now you should appreciate why $1$ is not
  allowed as a prime).
  \begin{enumerate}[label=(\alph*),resume]
    \item Using this fact, prove that $\sqrt{n}$ is irrational
    unless $n = m^2$ for some natural number $m$.
    \item Prove more generally that $\sqrt[k]{n}$ is irrational
    unless $n = m^k$
    \item Prove that there cannot be only finitely many
    prime numbers $p_1, p_2, \dots , p_n$ by considering
    $p_1\cdot p_2 \cdot \ldots \cdot p_n + 1$.
  \end{enumerate}
\end{pr}

\begin{solution} % 2.17 solved
  \begin{enumerate}[label=(\alph*)]
    \item Let $n = 2$, then it is a prime itself. Suppose
    that the argument holds for $n=1,\dots,k$. Hence,
    for $n = k + 1$, if $k + 1$ is a prime, we are done. If not,
    then $k + 1$ can be written as a product
    of two numbers $n_1$ and $n_2$ smaller than $k + 1$.
    By assumption, $n_1$ and $n_2$ can be rewritten as
    the product of primes: Hence, any number $n > 1$
    can be written as a product of primes.
    \item Suppose that $\sqrt{n} = \dfrac{p}{q}$, for
    any integer $p,q$. Then $p^2 = nq^2$; because factorization
    is unique and by \ref{2.17:a}, $nq^2$ can be expressed
    as a product of primes; each of which appears
    twice, and the same is true for $q^2$.
    This implies that $n = m^2$, for some natural $m$.
    \item Suppose that $\sqrt[k]{n} = \dfrac{p}{q}$, for
    any integer $p,q$. Then $p^k = nq^k$; by the same
    reasoning as above, $nq^k$ and $q^k$ can be expressed
    as product of primes; each of which appears $k$ times.
    This implies that $n = m^k$, for some natural $m$.
    \item The proof is by contradiction. Suppose there were
    only a finite number of primes $p_1,\dots,p_n$. Then
    $p_1 \cdot p_2 \cdot \ldots \cdot p_n + 1$ could not
    be a prime, but then it is not evenly divisible by
    any of $p_1,\dots,p_n$ but $1$ and itself: This is
    then a prime number!
    \begin{ab}
      BEWARE! This does not say that
      $p_1 \cdot p_2 \cdot \ldots \cdot p_n + 1$ is
      \note{definitely} a prime number. What if it is
      evenly divisible for some primes in
      $p_{n+1},p_{n+2},\dots$? For example:
      \begin{equation*}
        2 \cdot 3 \cdot 5 \cdot 7 \cdot 11 \cdot 13 + 1
        = 30031 = 59 \cdot 509
      \end{equation*}
      Therefore, $p_{n+1} \geq
      p_1 \cdot p_2 \cdot \ldots \cdot p_n + 1$.
    \end{ab}
  \end{enumerate}
\end{solution}

\begin{pr}[*] \label{2.18} % 2.18
  Prove that
  \begin{enumerate}[label=(\alph*)]
    \item \label{2.18:a} If $x$ satisfies
    \begin{equation*}
      x^n + a_{n-1}x^{n-1} + \dots + a_0 = 0,
    \end{equation*}
    for some integers $a_{n-1},\dots,a_0$, then $x$ is
    irrational unless $x$ is an integer.(Why is this
    a generalization of \autoref{2.17}?)
    \item $\sqrt{6} - \sqrt{2} - \sqrt{3}$ is irrational.
    \item $\sqrt{2} + \sqrt[3]{2}$ is irrational. Hint: Start
    by working out the first $6$ powers of this number.
  \end{enumerate}
\end{pr}

\begin{solution} % 2.18 solved
  \begin{enumerate}[label=(\alph*)]
    \item We need first to prove the following lemma,
    \begin{id}
      For any $p > 1$, if $p^n$ is divisible by a prime,
      so is $p$.
    \end{id}
    \renewcommand{\qedsymbol}{$\square$}
    \begin{proof}
      $p^n$ can be written as a product of primes; each
      of which appears for $n$ times. Since $p^n$
      is divisible by a prime, this prime appears as a factor
      of $p^n$ for $n$ times,
      which means $p$ is divisible by the prime.
    \end{proof}
    Suppose $x$ were rational, then $x = \dfrac{p}{q}$
    such that $p$ and $q$ are integers that have no common
    factors.
    Hence, the equation satisfying $x$
    \begin{equation*}
      \left(\frac{p}{q}\right)^n + a_{n-1}\left(\frac{p}{q}
      \right)^{n-1} +
      \dots + a_0 = 0
    \end{equation*}
    is equivalent to
    \begin{equation*}
      p^n + a_{n - 1}p^{n - 1}q + \dots + a_0q^n = 0
    \end{equation*}
    if and only if $q^n = 1$. Suppose $q \neq \pm1$, then
    by \autoref{2.17}, $q$ can be factored as the product
    of primes. Hence, $a_{n - 1}p^{n - 1}q + \dots + a_0q^n$
    must be divisible by one of those primes. Since the
    result is an integer, it is clear that $p^n$ must
    be also divisible by that prime, and note that $p > 1$.
    But this implies that $p$ must also be divisible
    by the prime: A contradiction that $p$ and $q$ have
    no common factors. Therefore, $q = \pm1$, and we
    conclude that $x$ is an integer.
    \par
    Now let $a_{n-1},\dots,a_1$ be $0$ and $k = -a_0$,
    we see that $\sqrt[n]{k} = x$ is irrational unless
    $k = x^n$ for some integer $x$ since $k$ is an integer.
    \item Let $x = \sqrt{6} - \sqrt{3} - \sqrt{2}$. Then
    \begin{IEEEeqnarray*}{rCl}
      x^2 & = & 11 + 2\sqrt{6}(1 - \sqrt{2} - \sqrt{3}) \\
      (x^2 - 11)^2 & = & 24(1 - \sqrt{2} - \sqrt{3})^2  \\
      x^4 - 22x^2 + 121 & = & 24(6 + 2x)                \\
      x^4 - 22x^2 - 48x - 23 & = & 0
    \end{IEEEeqnarray*}
    By \ref{2.18:a}, $x$ is either an irrational or an
    integer. We will show that the latter is impossible.
    Note that since $\sqrt{6}$ and $\sqrt{2} + \sqrt{3}$
    are positive and,
    \begin{equation*}
      (\sqrt{2} + \sqrt{3})^2 - 6 = 2\sqrt{6} - 1 > 0
    \end{equation*}
    Moreover,
    \begin{equation*}
      (\sqrt{2} + \sqrt{3})^2 = 5 + 2\sqrt{6} < 7 + 2\sqrt{6}
      = (1 + \sqrt{6})^2
    \end{equation*}
    Therefore, we conclude
    $0 < \sqrt{2} + \sqrt{3} - \sqrt{6} < 1$, which means
    that $x$ must be irrational.
    \item Observe that $\sqrt{2} + \sqrt[3]{2}$ satisfies
    \begin{equation*}
      x^6 - 6x^4 - 4x^3 + 12x^2 - 24x - 4 = 0
    \end{equation*}
    Therefore, it is either an irrational number or an
    integer, but $2 < \sqrt{2} + \sqrt[3]{2} < 3$: Hence,
    the former must be true!
  \end{enumerate}
\end{solution}

\begin{pr} % 2.19
  Prove Bernoulli's inequality: If $h > -1$, then
  \begin{equation*}
    (1 + h)^n \geq 1 + nh.
  \end{equation*}
  Why is this trivial if $h > 0$?
\end{pr}

\begin{solution} % 2.19 solved
  The proof is by induction. When $n = 1$, $1 + h = 1 + h$.
  Suppose the inequality holds for $n$, then for $n+1$,
  \begin{IEEEeqnarray*}{rCl}
    (1+h)^{n+1} = (1+h)^n(1+h) & \geq & (1 + nh)(1 + h)     \\
                               &  =   & 1 + h + nh + nh^2   \\
                               & \geq & 1 + (n + 1)h
  \end{IEEEeqnarray*}
  Note that without the condition $h > -1$, the first inequality
  sign will be reversed!
  \par
  If $h > 0$, expanding the left-hand side using the binomial
  theorem directly yields the result since
  $\displaystyle\sum_{k=2}^n \binom{n}{k} h^k \geq 0$.
\end{solution}

\begin{pr} % 2.20
  The Fibonacci sequence $a_1, a_2, a_3, \dots$ is defined
  as follows:
  \begin{IEEEeqnarray*}{rClr}
    a_1 & = & 1 \\
    a_2 & = & 1 \\
    a_{n} & = & a_{n - 1} + a_{n - 2} & \quad
    \text{for $n \geq 3$.}
  \end{IEEEeqnarray*}
  Prove that
  \begin{equation*}
    a_n = \frac{\left(\dfrac{1 + \sqrt{5}}{2}\right)^n
    - \left(\dfrac{1 - \sqrt{5}}{2}\right)^n}%
    {\sqrt{5}}
  \end{equation*}
  One way of deriving this astonishing formula is presented
  in Problem 24.15 % \autoref{24.15}
\end{pr}

\begin{solution} % 2.20 solved
  The proof is by complete induction. Let $n=1$, then
  $a_1 = 1$. Suppose now that the formula holds for
  $1,\dots,n$, then for $n+1$,
  \begin{IEEEeqnarray*}{rCl}
    a_{n + 1} & = & a_n + a_{n - 1}               \\
    & = & \frac{\left(\dfrac{1 + \sqrt{5}}{2}\right)^n
        - \left(\dfrac{1 - \sqrt{5}}{2}\right)^n}%
        {\sqrt{5}} +
        \frac{\left(\dfrac{1 + \sqrt{5}}{2}\right)^{n - 1}
        - \left(\dfrac{1 - \sqrt{5}}{2}\right)^{n - 1}}%
        {\sqrt{5}}                                 \\
   & = &  \frac{\left(\dfrac{1 + \sqrt{5}}{2}\right)^n
        \left(\dfrac{3 + \sqrt{5}}{1 + \sqrt{5}}\right)
       - \left(\dfrac{1 - \sqrt{5}}{2}\right)^n
        \left(\dfrac{3 - \sqrt{5}}{1 - \sqrt{5}}\right)
       }%
       {\sqrt{5}}                                   \\
  & = &  \frac{\left(\dfrac{1 + \sqrt{5}}{2}\right)^{n+1}
      - \left(\dfrac{1 - \sqrt{5}}{2}\right)^{n+1}}%
      {\sqrt{5}}
  \end{IEEEeqnarray*}
  where in the second equality,
  \begin{equation*}
    \frac{(3+\sqrt{5})(1-\sqrt{5})}{1-5} =
    \frac{1 + \sqrt{5}}{2}
  \end{equation*}
  and
  \begin{equation*}
    \frac{(3-\sqrt{5})(1+\sqrt{5})}{1-5} =
    \frac{1 - \sqrt{5}}{2}
  \end{equation*}
\end{solution}

\begin{pr} % 2.21
  The Schwarz inequality (\autoref{1.19}) actually has
  a more general form:
  \begin{equation*}
    \sum_{i=1}^n x_iy_i \leq
    \sqrt{\sum_{i=1}^n x_i^2}\sqrt{\sum_{i=1}^n y_i^2}
  \end{equation*}
  Give three proofs of this, analogous to the three proofs
  presented in \autoref{1.19}.
\end{pr}

\begin{solution} % 2.21 solved
  We will give three proofs just as in \autoref{1.19}
  \begin{enumerate}[label=(\alph*)]
    \item \label{2.21:a}
    \note{The first proof}: Note that the equality
    occurs when either $y_i = 0 \quad \forall i$ or
    $x_i = \lambda y_i \quad \forall i$ for $\lambda > 0$.
    Otherwise,
    \begin{IEEEeqnarray*}{rCl}
      0 & < & \sum_{i=1}^n (x_i - \lambda y_i)^2 \\
        & = & \lambda^2(\sum_{i=1}^n y_i^2)
        - 2 \lambda (\sum_{i=1}^n x_iy_i)
        + (\sum_{i=1}^n x_i^2)                   \\
        & = & \lambda^2
        - 2 \lambda \left(\frac{\displaystyle\sum_{i=1}^n x_iy_i}%
        {\displaystyle\sum_{i=1}^n y_i^2}\right)
        + \left(\frac{\displaystyle\sum_{i=1}^n x_i^2}%
        {\displaystyle\sum_{i=1}^n y_i^2}\right)
    \end{IEEEeqnarray*}
    This is the case only if
    \begin{IEEEeqnarray*}{rCl}
      \left(\sum_{i=1}^n x_iy_i\right)^2 & \leq &
      \sum_{i=1}^n x_i^2\sum_{i=1}^n y_i^2      \\
      \sum_{i=1}^n x_iy_i \leq \left|\sum_{i=1}^n x_iy_i\right|
                                         & \leq &
      \sqrt{\sum_{i=1}^n x_i^2}\sqrt{\sum_{i=1}^n y_i^2}
    \end{IEEEeqnarray*}
    This concludes our first proof.
    \item \note{The second proof:} Let
    \begin{align*}
      x = \frac{x_i}{\sqrt{\sum_{i=1}^n x_i^2}} &&
      y = \frac{y_i}{\sqrt{\sum_{i=1}^n y_i^2}} &&
      \text{for all $i=1,\ldots,n$}
    \end{align*}
    and note that $(x - y)^2 \geq 0$. Hence,
    \begin{align*}
      \frac{x_i^2}{\sum_{i=1}^n x_i^2} +
      \frac{y_i^2}{\sum_{i=1}^n y_i^2} \geq
      2 \cdot \frac{x_i y_i}{\sqrt{\sum_{i=1}^n x_i^2}%
      \sqrt{\sum_{i=1}^n y_i^2}} &&
      \text{for all $i=1,\ldots,n$}
    \end{align*}
    Summing up all $n$ inequalities yields the result.
    Notice also that equality occurs with the same
    conditions as above.
    \item \note{The third proof:} Notice that
    \begin{equation*}
      \left(\sum_{i=1}^n x_i^2\right)
      \left(\sum_{i=1}^n y_i^2\right) =
      \left(\sum_{i=1}^n x_i y_i\right)^2 +
      \sum_{\substack{i=1 \\ i\neq j}}^n
      \left(x_i y_j - x_j y_i\right)^2
    \end{equation*}
    This essentially delivers the result since
    $\sum_{\substack{i=1 \\ i\neq j}}^n
    \left(x_i y_j - x_j y_i\right)^2 \geq 0$
    for all terms, with the
    equality condition as in \ref{2.21:a}.
  \end{enumerate}
\end{solution}

\begin{pr} \label{2.22} % 2.22
  The result in \autoref{1.7} has an important generalization:
  If $a_1,\ldots,a_n \geq 0$, then the ``arithmetic mean''
  \begin{equation*}
    A_n = \frac{a_1 + \dots + a_n}{n}
  \end{equation*}
  and ``geometric mean''
  \begin{equation*}
    G_n = \sqrt[n]{a_1 \cdots a_n}
  \end{equation*}
  satisfy
  \begin{equation*}
    G_n \leq A_n
  \end{equation*}
  \begin{enumerate}[label=(\alph*)]
    \item Suppose that $a_1 < A_n$. Then some $a_i$ satisfies
    $a_i > A_n$\footnote{Since
    $A_n = \dfrac{a_1 + \dots + a_n}{n} < a_i$ where
    $a_i = max(a_1,\dots,a_n)$.}%
    ; for convenience, say $a_2 > A_n$. Let
    $\bar{a}_1 = A_n$ and let $\bar{a}_2 = a_1 + a_2
    - \bar{a}_1$. Show that
    \begin{equation*}
      \bar{a}_1 \bar{a}_2 \geq a_1 a_2
    \end{equation*}
    Why does repeating this process enough times eventually
    prove that $G_n \leq A_n$? When does this equality
    hold in the formula $G_n \leq A_n$?
  \end{enumerate}
  The reasoning in this proof is related to another
  interesting proof.
  \begin{enumerate}[label=(\alph*),resume]
    \item \label{2.22:b}
    Using the fact that $G_n \leq A_n$ when $n = 2$,
    prove, by induction on $k$, that $G_n \leq A_n$ for
    $n = 2^k$.
    \item For a general $n$, let $2^m > n$. Apply part
    \ref{2.22:b} to the $2^m$ numbers
    \begin{equation*}
      a_1,\dots,a_n,
      \underbrace{A_n,\dots,A_n}_\text{$2^m - n$ times}
    \end{equation*}
    to prove that $G_n \leq A_n$
  \end{enumerate}
\end{pr}

\begin{solution} % 2.22 solved
  \begin{enumerate}[label=(\alph*)]
    \item
    \begin{IEEEeqnarray*}{rCl}
      \bar{a}_1 \bar{a}_2 - a_1 a_2 & = &
      -A_n^2 + (a_1 + a_2)A_n - a_1 a_2   \\
                                    & = &
      (A_n - a_1)(a_2 - A_n) > 0
    \end{IEEEeqnarray*}
    since $a_1 < A_n < a_2$. Therefore,
    $\bar{a}_1 \bar{a}_2 \geq a_1 a_2$.
    \par
    If we let $\bar{a}_{k+1}=\sum_{i=1}^{k+1} a_i
    - (\sum_{i=1}^k \bar{a}_i)= kA_k + a_{k+1} - kA_k$,
    we easily prove that $G_n \leq \bar{G}_n$ by induction.
    Notice further that $\bar{A}_n = A_n$. Hence, it is
    sufficient to prove that $\bar{G}_n \leq \bar{A}_n = A_n$.
    This is achieved by complete induction: Let $\bar{a}_1
    = A_n$, then there is nothing to prove. Suppose for
    $\bar{a}_i = A_n$ for $i=1,\ldots,k$, the inequality
    holds, then for $\bar{a}_i = A_n$ for $i=1,\ldots,k,k+1$
    the inequality must also hold, which is an equality.
    The equality holds only for $\bar{a}_i = A_n$ for all $i > 2$
    since $\bar{G}_n < G_n$ for some $a_i \neq a_1$.
    \item If $k=1$, then $n = 2^1 = 2$ and there is nothing to prove.
    Suppose now that the inequality holds for $n=2^k$, then
    for $m = 2^{k+1} = 2n$,
    \begin{IEEEeqnarray*}{rCl}
      G_m = \sqrt[2n]{a_1 \cdots a_m} & = &
      \sqrt[n]{\sqrt{a_1 a_2} \cdots
      \sqrt{a_{m-1} a_{m}}}                    \\
                                      & \leq &
      \sqrt[n]{\frac{a_1 + a_2}{2} \cdot \dots \cdot
      \frac{a_{m-1} + a_{m}}{2}}
                                                \\
                                      & \leq &
      \frac{\dfrac{a_1 + a_2}{2} + \cdots
      + \dfrac{a_{m-1} + a_{m}}{2}}%
      {n}                                       \\
                                      &  =   &
      \frac{a_1 + \cdots + a_m}{2n} = A_m
    \end{IEEEeqnarray*}
    where in the first inequality, $G_n \leq A_n$ for
    $n = 2$ is used and in the second inequality
    the induction assumption is used for $m/2 = n$ terms.
    \item Let $l = 2^m - n$, then
    \begin{IEEEeqnarray*}{rCl}
      \sqrt[2^m]{a_1 \cdots a_n \cdot (A_n)^l} & \leq &
      \frac{a_1 + \dots + a_n + lA_n}{n + l}          \\
                                               &  =   &
      \frac{nA_n + lA_n}{n + l}                       \\
                                               &  =   &
      A_n                                             \\
      \Rightarrow a_1 \cdots a_n \cdot (A_n)^l & \leq &
      (A_n)^{n+l}                                     \\
      a_1 \cdots a_n                           & \leq &
      (A_n)^n                                         \\
      \Rightarrow G_n = \sqrt[n]{a_1 \cdots a_n}& \leq &
      A_n
    \end{IEEEeqnarray*}
  \end{enumerate}
\end{solution}

\begin{pr} \label{2.23} % 2.23
  The following is a recursive definition of $a^n$:
  \begin{align*}
    a^1 &= a, \\
    a^{n+1} &= a^n \cdot a.
  \end{align*}
  Prove, by induction, that
  \begin{align*}
    a^{n+m} &= a^n \cdot a^m, \\
    (a^n)^m &= a^{nm}.
  \end{align*}
\end{pr}

\begin{solution} % 2.23 solved
  The proof is by induction on $m$.
  \par
  For the first part, let $m = 1$, then
  $a^{n + 1} = a^n \cdot a^1$ by definition. Suppose we have
  $a^{n + k} = a^n \cdot a^k$, then we want to prove that
  \begin{equation*}
    a^{n + (k + 1)} = a^n \cdot a^{k + 1}
  \end{equation*}
  Hence, notice that $n + (k + 1) = (n + k) + 1$, and
  \begin{IEEEeqnarray*}{rCl}
    a^{(n + k) + 1} & = & a^{n + k} \cdot a \\
                    & = & a^{n} \cdot (a^{k} \cdot a) \\
                    & = & a^{n} \cdot a^{k + 1}
  \end{IEEEeqnarray*}
  where the first and third equality are by definition while
  the second one used the assumption.
  \par
  For the second part, let $m = 1$, then obviously $(a^n)^1
  = a^n$. Assume we have $(a^n)^k = a^{nk}$, then we want
  to prove,
  \begin{equation*}
    (a^n)^{(k + 1)} = a^{n(k + 1)}
  \end{equation*}
  Then
  \begin{IEEEeqnarray*}{rCl}
    (a^n)^{(k + 1)} & = & (a^n)^k \cdot a^n \\
                  & = & a^{nk}  \cdot a^n \\
                  & = & a^{n(k + 1)}
  \end{IEEEeqnarray*}
  where the first equality follows from definition;
  the second follows from assumption, and the third follows
  from the first part.
\end{solution}

\begin{pr} \label{2.24} % 2.24
  Suppose we know properties P1 and P4 for the natural
  numbers, but that multiplication has never been mentioned.
  Then the following can be used as a recursive definition of
  multiplication:
  \begin{align*}
    1     \cdot b &= b, \\
    (a+1) \cdot b &= a \cdot b + b.
  \end{align*}
  Prove the following (in the order suggested!):
  \begin{IEEEeqnarray*}{rCl}
    a \cdot (b + c) & = & a \cdot b + a \cdot c  \\
    a \cdot 1       & = & a,                     \\
    a \cdot b       & = & b \cdot a
  \end{IEEEeqnarray*}
\end{pr}

\begin{solution} % 2.24 solved
  We divide our proofs into three parts.
  \begin{itemize}
    \item $a \cdot (b + c) = a \cdot b + a \cdot c$
    \par
    The proof is by induction on $a$. Let $a = 1$, then
    by definition $1 \cdot (b + c) = 1 \cdot b + 1 \cdot c$.
    Assume $k \cdot (b + c) = k \cdot b + k \cdot c$.
    We want to prove that
    \begin{equation*}
      (k+1)(b+c) = (k+1)b + (k+1)c
    \end{equation*}
    Then
    \begin{IEEEeqnarray*}{+rCl+x*}
      (k+1)(b+c) &=& k(b+c) + 1 \cdot (b+c) & \text{by definition} \\
                 &=& (kb + b) + (kc + c)    & \text{by assumption, P1 and P4}  \\
                 &=& (k+1)b + (k+1)c        & \text{by P1}
    \end{IEEEeqnarray*}
    \item $a \cdot 1 = a$
    \par
    The proof is by induction on $a$. Let $a = 1$, then
    $1 \cdot 1 = 1$ by definition. Assume $k \cdot 1 = k$,
    then
    \begin{equation*}
      (k+1) \cdot 1 = k \cdot 1 + 1 \cdot 1 = k + 1
    \end{equation*}
    where the first equality is due to definition while
    the second one is of both assumption and definition.
    \item $a \cdot b = b \cdot a$
    \par
    The proof is by induction on $b$. Let $b = 1$, then
    $a \cdot 1 = 1 \cdot a = a$.
    Assume $a \cdot k = k \cdot a$. Then
    \begin{IEEEeqnarray*}{+rCl+x*}
      a \cdot (k + 1) &=& a \cdot k + a \cdot 1
      & \text{by the first part}                \\
      &=& a \cdot k + a & \text{by the second part}    \\
      &=& k \cdot a + a & \text{by assumption}         \\
      &=& (k + 1) \cdot a & \text{by definition}
    \end{IEEEeqnarray*}
  \end{itemize}
\end{solution}

\begin{pr} \label{2.25} % 2.25
  If we accept the real numbers as given, then the natural
  numbers can be \note{defined} as the real numbers of the
  form $1,1+1,1+1+1,$ etc. The whole point of this problem
  is to show that there is a rigorous mathematical way of
  saying ``etc.''
  \begin{enumerate}[label=(\alph*)]
    \item A set $A$ of real numbers is called \boldText{inductive}
    if
    \begin{center}
      \begin{minipage}{0.5\textwidth}
        \begin{enumerate}[label=(\arabic*)]
          \item $1$ is in $A$
          \item $k + 1$ is in $A$ whenever $k$ is in $A$.
        \end{enumerate}
      \end{minipage}
    \end{center}
    Prove that
    \begin{enumerate}[label=(\roman*)]
      \item $\mathbb{R}$ is inductive.
      \item The set of positive real numbers is inductive.
      \item The set of positive real numbers unequal to
      $\frac{1}{2}$ is inductive.
      \item The set of positive real numbers unequal to
      $5$ is not inductive.
      \item If $A$ and $B$ are inductive, then the set $C$
      of real numbers which are in both $A$ and $B$ is also
      inductive.
    \end{enumerate}
    \item A real number $n$ will be called a
    \boldText{natural number} if $n$ is in \note{every}
    inductive set.
    \begin{enumerate}[label=(\roman*)]
      \item Prove that $1$ is a natural number.
      \item Prove that $k + 1$ is a natural number if
      $k$ is a natural number.
    \end{enumerate}
  \end{enumerate}
\end{pr}

\begin{solution} % 2.25 solved
  \begin{enumerate}[label=(\alph*)]
    \item Let $P$ be the set of positive real numbers and
    $P_{n}$ be the set of positive real numbers
    not equal to $n$.
    \begin{enumerate}[label=(\roman*)]
      \item By definition, $\mathbb{R}$ is inductive.
      \item Suppose not. Assume $p \in P$.
      Then $p + 1 \notin P$ whenever
      $p \in P$. This implies $p \leq -1 < 0$: A contradiction.
      \item Suppose not. Then there exist some number $p$
      such that $p + 1 = \frac{1}{2}$, which implies
      $p = - \frac{1}{2}$: This contradicts $p \in P_{1/2}$.
      \item $4$ is in $P_5$ but $5$ is not in $P_5$.
    \end{enumerate}
  \end{enumerate}
\end{solution}
